### 2016-08-15 ms/ms_ma.tex
added the methods for algebraic connectivity

\subsection*{Network robustness}
Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness of the network to species
loss. Following \cite{Memmott2004}, we simulate the extinction of
plant species the subsequent extinction cascades of pollinator
species. Because the reproduction of plant species if facilitated by
active restoration efforts, it is unlikely the extinction of
pollinators would affect plant populations in the hedgerows. However,
plants ceasing to bloom, for example in response to drought, will
likely affect the pollinators that depend on them. Plants species were
eliminated based on their degree or abundance, and the number of
pollinators that secondarily went extinct is calculated. The area
below the extinction curve is used as a measure of network robustness. %Maybe cite the R function we used here?

>>>>

\subsection*{Network robustness}
Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness of the network to species
loss and to cascading effects. Following \cite{Memmott2004}, we simulate the extinction of
plant species the subsequent extinction cascades of pollinator
species. Because the reproduction of plant species if facilitated by
active restoration efforts, it is unlikely the extinction of
pollinators would affect plant populations in the hedgerows. However,
plants ceasing to bloom, for example in response to drought, will
likely affect the pollinators that depend on them. Plants species were
eliminated based on their degree or abundance, and the number of
pollinators that secondarily went extinct is calculated. The area
below the extinction curve is used as a measure of network robustness. %Maybe cite the R function we used here?
We also explored how the robustness to cascading effects changed as community assembled, using algebraic connectivity--- the second smallest eigenvalue of the Laplacian matrix \citep{fiedler1973algebraic}--- as a proxy for network robustness (e.g. Gaiarsa et al., submitted). Algebraic connectivity was first used to describe spectral properties of complex graphs other than ecological networks, and it is related to how difficult it is to turn a network into completely disconnected groups of nodes, or species \citep{fiedler1973algebraic, costa2007characterization}, and also to flows in . The larger the algebraic connectivity, the more robust a network is to perturbations (e.g. Gaiarsa et al., submitted).
